The Astropy Project

### 2017-11-30 main.tex

\python\footnote{\url{https://www.python.org/}} is an increasingly popular, general-purpose
programming language that is available under a permissive open source software license free of
charge for all major operating systems. The programming language has become especially popular
in the quantitative sciences, where researchers must simultaneously produce research, perform 
data analysis and develop software. A large part of this success owes itself to the vibrant 
community of developers and a continuously-growing ecosystem of tools, web services and stable
well-developed packages that enable easier collaboration on software development, easier 
writing and sharing of software documentation and continuous testing and validation of 
software. While the programming language provides support for array representation \& 
arithmetic \citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific 
computing \citep[\package{scipy};][]{scipy}, publication-quality plotting 
\citep[\package{matplotlib};][]{matplotlib}, tens of thousands of other high quality and easy 
to use packages are available which can help with tasks that are not astronomy specific but 
might be performed in the course of astronomical research, for example, interfacing with 
databases or statistical inferences. More recently, the development of package managers such as
Anaconda\footnote{\url{https://anaconda.org/}} have streamlined the installation process for
most packages significantly reducing the barrier to entry for using many such libraries.

The \astropy project aims to provide an open-source, open-development core
package (\astropypkg) and an ecosystem of \emph{affiliated packages} that
support astronomical functionality in the \python programming language.
The \astropypkg core package is now a feature-rich library of sufficiently
general tools and classes that supports the development of more specialized
code. An example of such functionality is reading and writing FITS files: it would be
time consuming and impractical for multiple groups to implement the FITS
standard \citep{FITS} and maintain software for such a general-purpose need.
Another example of such a common task is in dealing with representations of and
transformations between astronomical coordinate systems.

The \astropy project aims to develop and provide high quality code and
documentation according to the best practices in software development.
The project makes use of these tools to do so without central institutional
oversight.
The first public release of the \astropypkg package is described in
\cite{astropy}. Since then, the \astropypkg package has been
used in hundreds of projects, and the scope of the package has grown
considerably. At the same time, the community of astronomers
contributing to the project has grown tremendously and an ecosystem
of packages supporting or affiliated with the \astropypkg core has
developed.
In this paper, we describe the current status of the \astropy community and the
\astropypkg core package and discuss goals for future development.

@@

\subsection{Astropy development model}
% draft by Adrian PW and Erik T.
Code is contributed to the \astropypkg core package or modified through ``pull
requests'' (via \github) that often contain several \texttt{git} commits.
Pull requests may fix bugs, implement new features, or improve or modify the
infrastructure that supports the development and maintenance of the package.
Individual pull requests are generally limited to a single conceptual addition
or modification to make code review tractable.
Pull requests that modify or add code to a specific subpackage must be reviewed
and approved by one of the subpackage maintainers before it is merged into the
core codebase.
Bugs and feature requests are reported via the \github issue tracker and labeled
with a set of possible labels that help classify and organize the issues.
The development workflow is detailed in the \astropypkg
documentation.\footnote{\emph{How to make a code contribution},
\url{http://docs.astropy.org/en/stable/development/workflow/development_workflow.html}}

>>>>

\python\footnote{\url{https://www.python.org/}} is an increasingly popular, general-purpose
programming language that is available under a permissive open source software license free of
charge for all major operating systems. The programming language has become especially popular
in the quantitative sciences, where researchers must simultaneously produce research, perform
data analysis, and develop software. A large part of this success owes itself to the vibrant
community of developers and a continuously-growing ecosystem of tools, web services, and stable
well-developed packages that enable easier collaboration on software development, easier
writing and sharing of software documentation, and continuous testing and validation of
software. While the programming language provides support for array representation and
arithmetic \citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific
computing \citep[\package{scipy};][]{scipy}, and publication-quality plotting
\citep[\package{matplotlib};][]{matplotlib}, tens of thousands of other high-quality and easy-to-use
packages are available, which can help with tasks that are not astronomy specific but
might be performed in the course of astronomical research; e.g., interfacing with
databases or statistical inferences. More recently, the development of package managers such as
Anaconda\footnote{\url{https://anaconda.org/}} have streamlined the installation process for
most packages, significantly reducing the entry barrier for using many such libraries.

The \astropy project aims to provide an open-source and open-development core
package (\astropypkg) and an ecosystem of \emph{affiliated packages} that
support astronomical functionality in the \python programming language.
The \astropypkg core package is now a feature-rich library of sufficiently
general tools and classes that supports the development of more specialized
code. An example of such functionality is reading and writing FITS files: It would be
time consuming and impractical for multiple groups to implement the FITS
standard \citep{FITS} and maintain software for such a general-purpose need.
Another example of such a common task is in dealing with representations of and
transformations between astronomical coordinate systems.

The \astropy project aims to develop and provide high-quality code and
documentation according to the best practices in software development.
The project makes use of these tools to do so without central institutional
oversight.
The first public release of the \astropypkg package is described in
\cite{astropy}. Since then, the \astropypkg package has been
used in hundreds of projects and the scope of the package has grown
considerably. At the same time, the scientific community
contributing to the project has grown tremendously and an ecosystem
of packages supporting or affiliated with the \astropypkg core has
developed.
In this paper, we describe the current status of the \astropy community and the
\astropypkg core package and discuss goals for future development.

@@

\subsection{Astropy development model}
% draft by Adrian PW and Erik T.
Code is contributed to the \astropypkg core package or modified through ``pull
requests'' (via \github) that often contain several \texttt{git} commits.
Pull requests may fix bugs, implement new features, or improve or modify the
infrastructure that supports the development and maintenance of the package.
Individual pull requests are generally limited to a single conceptual addition
or modification to make code review tractable.
Pull requests that modify or add code to a specific subpackage must be reviewed
and approved by one of the subpackage maintainers before it is merged into the
core codebase.
Bugs and feature requests are reported via the \github issue tracker and labeled
with a set of possible labels that help classify and organize the issues.
The development workflow is detailed in the \astropypkg
documentation.\footnote{\emph{How to make a code contribution},
\url{http://docs.astropy.org/en/latest/development/workflow/development_workflow.html}}
